Long Term Monitoring of the Disintegrating Planet Candidate KIC 12557548 b

### 2017-07-20 ms.tex
Updated the observations and previous observations sections.

\begin{deluxetable}{lr}
\tablecaption{List of observations}\label{tab:obsList}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Comment} \\
\colhead{UT} & \\
 }
\startdata
2016-06-10 & Clouds \\
2016-06-12 & Clear \\
2016-06-14 & Clear \\
2016-07-12 & Clear \\
2016-07-14 & Mostly clear \\
2016-07-16 & Clear \\
\enddata
\tablenotetext{}{Summary of observations and conditions in this work.}
\end{deluxetable}

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.
Table \ref{tab:obsList} shows a summary of our observations and the UT dates.
We obtained photometry for 5 nights with good weather on the \sha\ system.

@@

\begin{deluxetable*}{lrrrr}
\tablecaption{List of published observations}\label{tab:obsList}
\tablewidth{0pt}
\tablehead{
\colhead{Date Start} &
\colhead{Date End} &
\colhead{Observatory} &
\colhead{Filter} &
\colhead{Reference(s)} \\
UT & UT & & & \\
 }
\startdata
2009-05-13 & 2013-05-11 & Kepler & Open CCD & \citet{borucki2010} \\
2013-07-14 & 2013-07-31 & William Herchel & $u'$, $g'$, $z'$/$i'$ & \citet{bochinski2015evolving} \\
2013-08-13 & 2013-09-03 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
2014-08-14 & 2013-09-04 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
2016-06-12 & 2016-06-12 & Kuiper & Harris R & This Work \\
2016-07-12 & 2016-07-16 & Kuiper & Harris R & This Work \\
\enddata
\tablenotetext{}{Summary of published photometric observations of \sha.}
\end{deluxetable*}

>>>>

\begin{deluxetable}{lr}
\tablecaption{List of observations}\label{tab:photSummary}
\tablewidth{0pt}
\tablehead{
\colhead{Date} &
\colhead{Comment} \\
\colhead{UT} & \\
 }
\startdata
2016-06-10 & Clouds \\
2016-06-12 & Clear \\
2016-06-14 & Clear \\
2016-07-12 & Clear \\
2016-07-14 & Mostly clear \\
2016-07-16 & Clear \\
\enddata
\tablenotetext{}{Summary of observations and conditions in this work.}
\end{deluxetable}

\section{Observations}
We observed \sha\ with the Mont4k imager on the 61-inch Kuiper observatory.
Table \ref{tab:photSummary} shows a summary of our observations and the UT dates.
We obtained photometry for 5 nights with good weather on the \sha\ system.

@@

In order to understand the long term behavior of the \sha\ system, we summarize the available published photometry in Table \ref{tab:prevObs}
The Kepler mission provided the longest time baseline with near continuous photometry for about 4 years in long cadence ($\sim$30 min) mode.
Following the failure of the reaction wheel, there were a few follow-up ground based observations.
\citet{bochinsky2015evolving} obtained multi-color simultaneous photometry ($u'$, $g'$ and $z'$) to characterize the dust in the system.
The ratio of the $g'$ to $z'$ transit depths indeed deviated from unity, which could be fit with an interstellar dust extinction law.
Overall, \citet{bochinisky2015evolving} observed 5 separate nights spanning the expected transit durations and detect 1 transit $\sim$1\% in $g'$ band, 1 transit $\sim$0.1\% in $g'$ band and 3 upper limits of < 0.03\% for the other nights.

For one of the flux dip events, the $g$ band photometry exhibited a deeper transit depth than the $z'$ band.
The ratio

\begin{deluxetable*}{lrrrr}
\tablecaption{List of published observations}\label{tab:prevObs}
\tablewidth{0pt}
\tablehead{
\colhead{Date Start} &
\colhead{Date End} &
\colhead{Observatory} &
\colhead{Filter} &
\colhead{Reference(s)} \\
UT & UT & & & \\
 }
\startdata
2009-05-13 & 2013-05-11 & Kepler & Open CCD & \citet{borucki2010} \\
2013-07-14 & 2013-07-31 & William Herchel & $u'$, $g'$, $z'$/$i'$ & \citet{bochinski2015evolving} \\
2013-08-13 & 2013-09-03 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
2014-08-14 & 2013-09-04 & IRTF & $r'$, NIR spectroscopy & \citet{schlawin2016kic1255} \\
2016-06-12 & 2016-06-12 & Kuiper & Harris R & This Work \\
2016-07-12 & 2016-07-16 & Kuiper & Harris R & This Work \\
\enddata
\tablenotetext{}{Summary of published photometric observations of \sha.}
\end{deluxetable*}
